---
title: "wids_dataXB_eda"
team: "Data XB"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library-packages}
library(tidyverse)
library(patchwork)
library(dplyr)
```

```{r read-dataset}
#a csv file on every variable's meaning
varDict <- read.csv("widsdatathon2021/DataDictionaryWiDS2021.csv") 

varDict
#EDA this dataset
Diabetes <- read.csv("widsdatathon2021/TrainingWiDS2021.csv") 

```

###EDA Question & TO DOs
What are the missing values and their percentage in each column?
  -How values should we use to fill in the NAs?
What are variables related to diabetes?
  -Every BMI-related variables?
  -Ethnicity?Age?
  -Do we use every chemical variables (albumin, calcium...) in our model?
What columns can we drop? 
  -every ID
  

```{r glimpse-dataset}
glimpse(Diabetes)
```


```{r diabetes_by_gender}
Diabetes%>%
  filter(!is.na(gender))%>%
  ggplot(aes(x = gender, fill = factor(diabetes_mellitus)))+
  geom_bar(position = "fill")
```

```{r diabetes-ethnicity}
Diabetes%>%
  ggplot(aes(x = ethnicity, fill = factor(diabetes_mellitus))) + 
  geom_bar(position = "fill")

copyD <- Diabetes%>%
  filter(!is.na(ethnicity))%>%
  mutate(African = ifelse(ethnicity == "African American", 1, 0 ), 
         Caucasian = ifelse(ethnicity == "Caucasian", 1, 0 ), 
         Asian = ifelse(ethnicity == "Asian", 1, 0 ), 
         Hispanic = ifelse(ethnicity == "Hispanic", 1, 0 ), 
         Native_Am = ifelse(ethnicity == "Native American", 1, 0 ), 
         Other = ifelse(ethnicity == "Other/Unknown", 1, 0))

glimpse(copyD)
```

**Percentage of NAs in each Column**
It seems that many columns have NA percentage greater 70%, should we drop these
columns when we train the model? 

```{r missing-in-each-column}
colMeans(is.na(Diabetes))%>%
  kable()
```

```{r test-how-to-write-function}
#this function was created as a review on how to write function in R. Has no 
#actual meaning to this dataset
col_classes <- function(df) {
    lapply(df, function(x) paste(class(x), collapse = ','))
}

col_classes(Diabetes)
class(col_classes(Diabetes))
```

```{r get-colName-with-great-NA-percent}
#Not sure how to write a function to get the names of columns with a great 
#percentage of NAs. will work on this. 

check_per <- function(y){
  if((sum(is.na(y))/nrow(y)) > 0.7) {return (TRUE)} 
  return (FALSE)
}

remove_col <- function(df){
  mapply(df, function(x) paste(check_per(x)))
}
```



